---
title: "Anova and Diagnostics"
author: "Emmenta Janneh"
date: "2024-02-17"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(broom)
library(car) # companion of applied regression

hibbs <- read_csv("https://dcgerard.github.io/stat_415_615/data/hibbs.csv")
```

To do an ANOVA approach, first fit the linear model, then use the `Anova()` function from the `car` package.

```{r}
lm_hibbs <- lm(vote ~ growth, data = hibbs)
Anova(lm_hibbs)
```

| Value   | Meaning         | More          |
|---------|-----------------|---------------|
| 273.63  | SSE(R) - SSE(F) | SSR also SSTO |
| 198.27  | SSE(F)          | SSE           |
| 1       | df(R) - df(F)   |               |
| 14      | df(F)           |               |
| 19.321  | F-Statics       |               |
| 0.00061 | P-Value         |               |

Var = SSE(F) / df(F)

R has an `anova()` function, and we will use it, nut it is less useful in multiple linear regression.
```{r}
anova(lm_hibbs)
```

Use `glance()` to get R^2 in R
```{r}
glance(lm_hibbs)
```
57.98% of the variability in incumbent vote-share was explained by economic growth.

To make a fits vers residuals plot, get the fitted values and the residuals with `augment()`. 
Make a scatterplot of `.fitted` versus the `.resid` variables
```{r}
a_hibbs <- augment(lm_hibbs)
ggplot(a_hibbs, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_hline(yintercept = 0)
```

For sandwich estimate, use the `lmtest` and `sandwich` packages
```{r}
library(lmtest)
library(sandwich)
## vcon. tells the software how to estimate the standard errors
## vconHC is a function to estimate sandwich standard errors (Heteroskedastic Consistent)
cout <- coeftest(lm_hibbs, vcon. = vcovHC)
tidy(cout)
```
```{r}
tidy(lm_hibbs)
```

Only make qq-plots of residuals. To do so, use the `sample` aesthetic in `ggplot()`, and use `geom_qq()`.

```{r}
ggplot(a_hibbs, aes(sample = .resid)) +
  geom_qq() + 
  geom_qq_line()
```

Only check normality last, because other violations will result in non-normal looking QQ-plots.


