---
title: "Homework_4"
author: "Emmenta Janneh"
date: "2024-02-11"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(broom)
```

## Conceptual Exercises

1.  The standard error of β1 would decrease when a new observational unit is obtained with Xnew = Xmean. When Xnew = Xmean, the distance of each data point from the mean, Xi - Xmean, remains the same for all data points, including the new one. Therefore, the denominator of the formula remains constant.

    Since the denominator remains constant and Var is also assumed to be constant, the standard error SE would decrease as n ( the sample size) increases with the addition of the new observational unit.

2.  

    ```{r}
    2 * pt(-7.52, df = 13)
    0.997 / 0.111
    ```

    \## \# A tibble: 2 x 5\
    \## term estimate std.error statistic p.value\
    \## \<chr\> \<dbl\> \<dbl\> \<dbl\> \<dbl\>\
    \## 1 (Intercept) 8.39 1.11 7.52 `0.00000437`\
    \## 2 Years 0.997 0.111 `8.982` 0.000000618

3.  

    ```{r}
    estimate <- c(8.39, 0.997)
    std_error <- c(1.11, 0.111)
    statistic <- c(7.52, 8.982)
    df <- 15 - 2
    t_critical <- qt(0.975, df)

    lower_ci <- estimate - t_critical * std_error
    upper_ci <- estimate + t_critical * std_error

    ci_data <- data.frame(term = c("(Intercept)", "Years"),
                          lower_ci = lower_ci,
                          upper_ci = upper_ci
                          )
    ci_data

    ```

## Wheatears
```{r}
library(Sleuth3)
data("ex0727")
data("ex0727")
wheat <- ex0727
glimpse(wheat)
```

```{r}
lmout <- lm(Mass ~ Tcell, data = wheat)
ggplot(wheat, aes(x = Tcell, y = Mass)) + 
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```


1. 

```{r}
n <- nrow(wheat)
n
tidy(lmout, conf.int = TRUE)
```

Form the above information, we have a positive linear association between Tcell and Mass. `3.91` is the y-intercept of the regression line. Birds with `1mm` higher Tcell are estimated to carry on average `10.2g` higher stone mass (95% confidence interval of `3.3g` lower to `17.1g` higher). With a strong evidence that this association is not due to chance alone *(p = 0.006, n = 21)*.

2. 
```{r}
newbird <- data.frame(Tcell = c(0.35))
predict(object = lmout, newdata = newbird, interval = "confidence") %>% cbind(newbird)
```
We estimate that a bird with Tcell of 0.35mm can carry on average a stone with mass `7.5g` (95% confidence interval of 6.8g lower to 8.1g higher).

3. 
```{r}
newbird <- data.frame(Tcell = c(0.2))
predict(object = lmout, newdata = newbird, interval = "confidence")
```

Birds with 0.2mm Tcell are estimated to carry on average `5.9g` mass of stone (95% confidence interval of 4.9g lower to 7.0g higher mass).

4. 
```{r}
advbird <- data.frame(Tcell = c(20))
predict(object = lmout, newdata = advbird, interval = "predict")
```

We estimate that a \"super\" bird with Tcell of 20mm can carry on average `207.2g` (95% prediction interval of 71.5g lower to 342.9g higher).