---
title: "inference"
author: "Emmenta Janneh"
date: "2024-02-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(broom)

hibbs <- read.csv("https://dcgerard.github.io/stat_415_615/data/hibbs.csv")
lm_hibbs <- lm(vote ~ growth, data = hibbs)
tidy(lm_hibbs)
```

```{r}
lm_mtcars <- lm(mpg ~ drat, data = mtcars)
tidy(lm_mtcars)
```

```{r}
7.678 / 1.507  ## 5.096

nrow(mtcars) ## n = 32

2 * pt(-5.096, df = 30)  ## 0.00001776
```

To get a confidence interval in R use `conf.int = TRUE` in `tidy()`.
```{r}
tidy(lm_hibbs, conf.int = TRUE)
```

Let's use the p-value and the confidence interval to make a final report of the hibbs data.

We estimate that elections with 1 pp more growth have 3.1 pp higher vote share for the incumbent persident on average (95% CI of 1.6 pp to 4.6 pp higher). We have strong evidence of the linear association between economic growth and incumbent vote share (p-value = 0.00061, n = 16).

To get point-wise confidence interval in R, first fit the linear model, then create new data at the point you want the interval, then use the `predict()` function with `interval = "confidence"`.

```{r}
lm_hibbs
newdf <- data.frame(growth = c(1, 2))
predict(lm_hibbs, newdata = newdf, interval = "confidence")
predict(lm_hibbs, newdata = newdf, interval = "predict")
```

Years with 1% economic growth are estimated on average to have 49.3% incumbent vote-share (95% CI 46.9% to 51.7%)

We predict that an election year with 1% growth will have 49.3% incumbent vote share (95% predicition interval of 40.9% to 57.7%)