---
title: "Homework01"
author: "Emmenta Janneh"
date: "2024-01-18"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

## R Basic
1. Load these data into R, directly using the URL (i.e., don’t download it first to load it into R). Call the resulting data frame cdi.
```{r}
cdi <- read.csv("https://dcgerard.github.io/stat_415_615/data/cdi.csv")
head(cdi)
```

2. reate a new variable called log_capita_income, which is the log-transformed capita_income. Make sure this new variable is present in the cdi data frame.
```{r}
cdi <- mutate(cdi, log_capita_income = log(cdi$capita_income))
head(cdi)
```

3. Use R to calculate the mean and standard deviation of area.
```{r}
area_mean <- mean(cdi$area)
area_sd <- sd(cdi$area)

area_mean
area_sd
```

4. Rename the pop variable to population. Make sure the cdi data frame has been modified.
```{r}
cdi <- rename(cdi, population = pop)
head(cdi)
```

5. Use filter() to print out just the rows from Delaware.
```{r}
filter(cdi, county == "Delaware")
```

6. Use an appropriate plot (via {ggplot2}) to explore the relationship between capita_income
and unemployment. Describe the relationship in a couple of sentences.
```{r}
ggplot(cdi, aes(x = unemployment, y = capita_income)) + 
  geom_point()
```
The scatterplot shows counties with less unemployment rate has much higher capital_income than counties with higher unemployment rate. Although counties with lower unemployment also have lower capita_income, this can be explained by other influencing factors other that unemployment rate.

7. Use an appropriate plot (via {ggplot2}) to explore the relationship between capita_income
and region
```{r}
ggplot(cdi, aes(x = region, y = capita_income)) +
  geom_boxplot()
```

## Miscillaneous
```{r}
x <- seq(1, 100, by = 3)
```

1. The sum of the log of the values of x
```{r}
sum(log(x))
```

2. The log of the sum of the values of x
```{r}
log(sum(x))
```

**Are these values the same?**
*NO, the vales are not the same, question one is looking for the addition of the log of the values of x, while question 2 is looking for the log of the sum of all x values.
