---
title: "Lab_01-1"
author: "Emmenta Janneh"
date: "2024-01-17"
output: pdf_document
urlcolor: "blue"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

# Lab 01-1

Load the CDI dataset into R, saving the data frame in a variable called `cdi`.

```{r}
cdi <- read_csv("https://dcgerard.github.io/stat_415_615/data/cdi.csv")
```

Use a function that provides a rough glimpse at these data.

```{r}
glimpse(cdi)
```

Calculate the mean and standard deviation of the population of the counties

```{r}
pop_mean <- mean(cdi$pop)
pop_mean

pop_sd <- sd(cdi$pop)
pop_sd
```

Convert the `pop` variable to be in units of 100,000 individuals (so 1 corresponds to 100,000, 2 corresponds to 200,000, ect).

```{r}
cdi <- mutate(cdi, pop = pop/100000)
glimpse(cdi)
```

Use an appropriate plot to explore the association between population and number of physicians.

```{r}
ggplot(cdi, aes(x = physicians, y = pop)) +
  geom_point()
```

Use an appropriate plot to explore the association between region and population

```{r}
ggplot(cdi, aes(x = region, y = pop)) +
  geom_boxplot()
```

Use an appropriate plot to explore the association between population and number of physicians in each region.

```{r}
ggplot(cdi, aes(y = pop, x = physicians)) + 
  geom_point() +
  facet_grid(~ region)
```

Create four datasets, one for each region.

```{r}
cdi_NC <- filter(cdi, region == "NC")
head(cdi_NC)

cdi_NE <- filter(cdi, region == "NE")
head(cdi_NE)

cdi_S <- filter(cdi, region == "S")
head(cdi_S)

cdi_W <- filter(cdi, region == "W")
head(cdi_W)
```

Reproduce the following using markdown:

1.  It was the best of times,
2.  It was the worst of times,

-   **It was the age of wisdom**,
-   *it was the age of foolishness*,
-   [it was the epoch of belief](https://www.youtube.com/watch?v=dQw4w9WgXcQ)...
