---
title: "lectuer_1_note"
author: "Emmenta Janneh"
date: "2024-01-17"
output: pdf_document
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
x <- 1
x
```

These are simple r code for rmarkdown

# # - This is header 1
## - double # is for header 2

This is *italic*
This is **bold**

- This is item 1
- This is item 2
- This is item 3

1. enumerated item 1
2. enumerated item 2
3. enumerated item 3

<https://www.google.com> is a clickable link

[this is a hyperlink](https://www.google.com)



# Plotting and visualization
```{r}
data("mpg", package = "ggplot2")
glimpse(mpg)
```

```{r}
ggplot(mpg, aes(x = hwy, y = cty, color = class))
```

## The BEST plot for each situation:
 - One quantitative variables, look at its distribution: histogram
 - One categorical variable, look at its distribution: bar
 - Two quantitative, look at their association: scatterplot
 - One quantitative and one categorical, look st their association: boxplot
 - Two categorical: two-way table
 
## One quantitative
```{r}
ggplot(mpg, aes(x = hwy)) + 
  geom_histogram(bins = 15)
```
 
## One categorical 
```{r}
ggplot(mpg, aes(x = class)) + 
  geom_bar()
```

## Two quantitative 
```{r}
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point()
```


We can fix overplotting when there are overlaps with geom_jitters()
```{r}
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_jitter()
```


You can vie a smoother with geom_smooth()
```{r}
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```

## Boxplots for discrete x and continuous y
```{r}
ggplot(mpg, aes(x = class, y = hwy)) + 
  geom_boxplot()

ggplot(mpg, aes(x = hwy, y = class)) + 
  geom_boxplot()
```

You can color code by a third variable

```{r}
ggplot(mpg, aes(x = displ, y = hwy, color = class)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```











